Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
paper update

\title{SafeServe: User-Editable Websites in Haskell}
\author{
        John Hiesey \\
        jhiesey@cs.stanford.edu
}
\date{\today}

@@

\section{Results}\label{results}
In this section we describe the results.

@@

>>>>

\title{Incorporating Gyroscope Information in Gesture Recognition}
\author{
        John Hiesey \\
        jhiesey@cs.stanford.edu
}
\date{\today}

@@

\section{Results}\label{results}
\paragraph{Clustering approach}
Our initial approach of clustering on all training data together
worked reasonably well.  When running on all 5 sample gestures and
with the HMM enabled, we got an an accuracy of 89.6\%.

However, on the same data, our cluster-matching algorithm combined with
an HMM reaches 94.6\%.  We also observed similar improvements with examples,
as seen in the data.

\paragraph{HMM}
Although we found a few examples where the cluster-matching algorithm
benefits from using a Hidden Markov Model, in most real-world examples
there is little benefit.  When running on all of the training data,
we

@@

\section{Future Research}
Try our new algorithm with single clustering
